Modelling low Mach number stellar hydrodynamics with MAESTROeX

### 2019-10-02 astronum_2019_MAESTROeX/astronum-maestroex.tex
comment

New versions of the codes are released on the first of each month, and are archived on Zenodo\footnote{\url{https://zenodo.org/}}. This also provides us with DOIs (digital object identifiers), further enhancing the reproducibility of our results and ensuring the sustainability of the codes used to produce them.

>>>>

\MarginPar{I didn't think we did Zenodo yet}
New versions of the codes are released on the first of each month, and are archived on Zenodo\footnote{\url{https://zenodo.org/}}. This also provides us with DOIs (digital object identifiers), further enhancing the reproducibility of our results and ensuring the sustainability of the codes used to produce them.
